Dynamical Stochastic Approximation Monte Carlo

### 2018-02-26 papers/histogram/sad.tex
updated paper and changed colors.py to order/include methods when plotting.

For the square-well fluid, our simulations treat systems with a
well-width of $\text{ww} = 1.30$ and a filling fraction of either
$\text{ff} = 0.10, 0.20$ or $\text{ww} = 0.20$.  The simulation explores the
energy space of the system down to a reduced temperature of
$T_{\text{min}} = 0.2$.  All simulations lead to the minimum important
energy $E_{\text{min}}$ and maximum entropy state $S_{\text{max}}$
being calculated (with the exception of the WL-TMMC method where both
of these parameters are needed a priori).  In the sections below, we
examine systems with different particles numbers and filling fractions.

~\jpsays{Add N50 ff0.1 and N50 ff0.3 and remove sticky-wall!}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:avgS-30x4}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_10-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:avgS-60x8}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lv/ww1_30-ff0_22-100x10-max-entropy-error}
  \caption{The average entropy error for each method is shown with
    WL-TMMC using a cutoff of 10$^{-10}$ serving as the
    standard.}\label{fig:avgS-100x10}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-mean-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}

\subsubsection{A $30\times4\times4$ $(N = 25)$ system with a sticky
wall}
In order to determine how the various methods scale with size,
simulations are run for systems with different particle numbers.  For
the $N = 25$ system, a sticky-wall is added to ensure that we see the
liquid and vapor phase separation.

A system is configured with dimensions $x = y = 4\sigma$ and $z =
30\sigma$.  A filling fraction $\text{ff} = 0.22$ is chosen which
yields $N = 25$ particles in the rectangular system.  These particles
are randomly inserted into the system and random moves are proposed
(with a translation scale $\delta_0 = 0.05$). The boundaries in $x$ and
$y$ are periodic while the $z$-axis is not periodic.  A sticky-wall is
inserted along the $z$-axis at one end to promote phase separation.
~\jpsays{should we include a sticky-wall.py plot or something else or
are we not going to talk about phase separation in this paper?}

We use the entropy error vs iterations as a metric to compare
simulation runtimes.  Simulations that take more iterations to reach
the same entropy error as a different method take longer to converge.
This behavior is seen in Fig.~\ref{fig:avgS-30x4}.
~\jpsays{SAD appears to do pretty well as does WL-TMMC for a cutoff of $10^{-10}$
although this seems to depend on what is used as the `standard'.}

@@

Figure~\ref{fig:N50-mean-error} shows a system consisting of 50 atoms
are placed in a periodic simple cubic unit cell with lattice constant
chosen to give a filling fraction of 0.20.  These particles are
randomly inserted into the system and random moves are proposed (with
a translation scale $\delta_0 = 0.05$).

\subsubsection{A $60\times8\times8$ $(N = 202)$ system with a sticky
wall}

A system is configured with dimensions $x = y = 8\sigma$ and $z =
60\sigma$.  A filling fraction $\text{ff} = 0.22$ is chosen which
yields $N = 202$ particles in the rectangular system.  These particles
are randomly inserted into the system and random moves are proposed
(with a translation scale $\delta_0 = 0.05$). The boundaries in $x$ and
$y$ are periodic while the $z$-axis is not periodic.  A sticky-wall is
inserted along the $z$-axis at one end to promote phase separation.

\subsubsection{A $100\times10\times10$ $(N = 525)$ system with a sticky
wall}

A system is configured with dimensions $x = y = 10\sigma$ and $z =
100\sigma$.  A filling fraction $\text{ff} = 0.22$ is chosen which
yields $N = 525$ particles in the rectangular system.  These particles
are randomly inserted into the system and random moves are proposed
(with a translation scale $\delta_0 = 0.05$). The boundaries in $x$ and
$y$ are periodic while the $z$-axis is not periodic.  A sticky-wall is
inserted along the $z$-axis at one end to promote phase separation.

\subsubsection{A Tanner dimensions? $(N = 500)$ system with no sticky
wall}

A system is configured with dimensions $x = y = z = 19\sigma?$.  A
filling fraction $\text{ff} = 0.30$ is chosen which yields $N = 500$
particles in a cubical system.  These particles are randomly inserted
into the system and random moves are proposed (with a translation scale
$\delta_0 = 0.05$). The boundaries in $x$ and $y$ are periodic while
the $z$-axis is not periodic.  A sticky-wall is not inserted along the
$z$-axis.

>>>>

For the square-well fluid, our simulations treat systems with a
well-width of $\text{ww} = 1.30$ and a filling fraction of either
$\text{ff} = 0.10, 0.20,$ or $0.30$.  The simulation explores the
energy space of the system down to a reduced temperature of
$T_{\text{min}} = 0.2$.  All simulations lead to the minimum important
energy $E_{\text{min}}$ and maximum entropy state $S_{\text{max}}$
being calculated (with the exception of the WL-TMMC method where both
of these parameters are needed a priori).  In the sections below, we
examine systems with different particles numbers and filling fractions.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:N50-ff0.3-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_10-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:N50-ff0.1-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-ff0.2-max-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}

\subsubsection{A periodic system with 10\% filling fraction and $(N = 50)$}
In order to determine how the various methods scale with size,
simulations are run for systems with different particle numbers. A filling
fraction $\text{ff} = 0.10$ is chosen which yields $N = 50$ particles
in the cubical system.  These particles are randomly inserted into the
system and random moves are proposed (with a translation scale
$\delta_0 = 0.05$). The boundaries in $x$ and $y$ are periodic while
the $z$-axis is not periodic.

We use the maximum entropy error vs iterations as a metric to compare
simulation runtimes and overall convergence.  Simulations that take
more iterations to reach the same entropy error as a different method
take longer to converge. This behavior is seen in
Fig.~\ref{fig:N50-ff0.1-max-error}.

@@

Figure~\ref{fig:N50-ff0.2-max-error} shows a system consisting of 50 atoms
that are placed in a periodic simple cubic unit cell with lattice constant
chosen to give a filling fraction of 0.20.  These particles are
randomly inserted into the system and random moves are proposed (with
a translation scale $\delta_0 = 0.05$).

\subsubsection{A periodic system with 30\% filling fraction and $N = 50$}

Figure~\ref{fig:N50-ff0.3-max-error} shows a system consisting of 50 atoms
that are placed in a periodic simple cubic unit cell with lattice constant
chosen to give a filling fraction of 0.30.  These particles are
randomly inserted into the system and random moves are proposed (with
a translation scale $\delta_0 = 0.05$).

\subsubsection{A periodic system with 30\% filling fraction and $N = 500$}

A system is configured with dimensions $x = y = z = 19\sigma$.  A
filling fraction $\text{ff} = 0.30$ is chosen which yields $N = 500$
particles in a cubical system.  These particles are randomly inserted
into the system and random moves are proposed (with a translation scale
$\delta_0 = 0.05$). The boundaries in $x$ and $y$ are periodic while
the $z$-axis is not periodic.
